---
title: "Week 3 Day 3 homework"
output: html_notebook
---
```{r}
#install.packages("rtweet")
library(rtweet)
library(tidyverse)
```

Q1. Load data, check number of rows & columns. List all variable names.
```{r}
code_clan_tweets <- read_csv("data/code_clan_tweets.csv") # load data
dim(code_clan_tweets) #check dimensions - there are 234 rows and 27 columns of data
names(code_clan_tweets) # list all variable names
```

Q2. Summarise the number of likes (var = favorite_count). Check for outliers using boxplot.
```{r}
num_of_likes <- code_clan_tweets %>%
  select(tweet_id, text, favorite_count) %>% # select columnds for easier readability
  arrange(desc(favorite_count)) %>% #arrange in descending order by favorite_count
  ggplot(aes(x = tweet_id, y = favorite_count)) + # plot tweet_it on horizontal (-) axis and favorite_count on vertival (|) axis
  geom_boxplot() + 
  coord_flip() # flip the chart on its side for easier readability

num_of_likes
```

Q3. Find the total of tweets stored in favorite_count, don't count retweeted (is_quote).
```{r}
total_favourites <- code_clan_tweets %>%
  select(tweet_id, favorite_count, is_quote) %>% # select columns for easier readability
  filter(is_quote == FALSE, favorite_count !=0) %>% # filter out tweets which were re-quoted and those that were not favorited
  summarise(total_favourites = n()) # get total number of tweets
total_favourites
```

Q4. Get the mean number of retweets (retweet_count), group by source used to send the tweet. Do not count is_quote tweets.
```{r}
mean_retweets <- code_clan_tweets %>%
  select(source, retweet_count, is_quote) %>%
  filter(is_quote == FALSE) %>%
  group_by(source) %>%
  summarise(unique(source), mean_retweets = round(mean(retweet_count), 0)) %>% #use unique() to show each source only once
  arrange(desc(mean_retweets))

mean_retweets

```
Q5. Get total of favorite_count, for each media type, arrange by likes descending. Asume that media = text where media type is not listed.
```{r}
total_fav_count <- sum(code_clan_tweets$favorite_count)
total_fav_count

favourite_count_total <- code_clan_tweets %>%
  select(media_type, favorite_count) %>%
  mutate(media_type = replace_na(media_type, "text")) %>% #replace NA media_type values with "text"
  group_by(media_type) %>%
  summarise(media_type = unique(media_type), total_favourited = sum(favorite_count)) %>%
  arrange(desc(total_favourited))

favourite_count_total
```

Q6. Find average number of chars contained in CodeClan tweets.
```{r}
mean_char_num <- code_clan_tweets %>%
  mutate(text, num_chars = str_length(text)) %>%
  drop_na(num_chars) %>%
  select(text, num_chars) %>%
  summarise(average_tweet_length = round(mean(num_chars), 0))

mean_char_num
```
Q7. Load CodeClan info file and join on to tweets dataframe
```{r}
code_clan_info <- read_csv("data/code_clan_info.csv")

joined_tweets <- code_clan_info %>%
  left_join(code_clan_tweets, code_clan_info, by = "tweet_id")

joined_tweets
```

Q8. create codeclan_hashtags that contain only the tweet ID and hashtag in lowercase. keep only tweets with hashtags.
```{r}
codeclan_hastags <- joined_tweets %>%
  select(tweet_id, hashtags, text) %>%
  drop_na(hashtags) %>%
  mutate(hashtags = tolower(hashtags))

codeclan_hastags
```

Q9. Find all instances where values begin with c( inside hashtags.
```{r}
c_hashtags <- codeclan_hastags %>%
  flatten(.,.hashtags) %>%
  str_detect("c\\(")
c_hashtags
```


