---
title: "Gleb V homework 2020-07-07"
output: html_notebook
---
I created database wrestling using terminal command "createdb wrestling", then seed it using script "psql -d wrestling -f wrestling.sql" and to check that it has worked correctly, I run "psql -d wrestling -f db_query.sql". The file db_query.sql has the following script inside: "SELECT * FROM wrestlers. 
------------
Create a connection to the local wrestling database from R.
Pass the argument max.con = 2 to PostgreSQL() to make sure you don’t have too many simultaneous connections. We’ll be setting up a local connection and perhaps a remote connection, hence ‘2’.
Remember to add a separate ‘disconnect’ block of code. We’ll write queries between the ‘connect’ and ‘disconnect’ blocks.

```{r}
library(RPostgreSQL) #import psql library
credentials_location <- paste0(Sys.getenv("HOME"),"/credentials.R") #get file path to credentials.
source(credentials_location) #source in credentials
```
```{r}
#create db connection
wrestling_db_connection <- dbConnect(drv = PostgreSQL(max.con = 2), user = postgresql_username, password = postgresql_password, dbname = 'wrestling', host = 'localhost')
```
```{r}
dbListTables(conn = wrestling_db_connection) #check what table names are contained in the database
dbListFields(conn = wrestling_db_connection, name = "wrestlers")#check which fields (columns) are contained in the database. ¡NB! even though "wrestlers" is the only table in this database, name has to specified, otherwise the function returns an error.
```
Using the R connection you just created, write and execute a SQL query to return all the wrestlers in the wrestlers table.
```{r}
wrestling_data <- dbGetQuery(conn = wrestling_db_connection, statement = 
                               "SELECT * FROM wrestlers")
wrestling_data
```
Explore the columns stored in the table. State which data type you think each column stores.
```{r}
str(wrestling_data)
```
Use your credentials to establish a connection from R to the remote database.
```{r}
wrestling_remote_db_connection <- dbConnect(drv = PostgreSQL(max.con = 2), user = remote_omni_postgresql_username, password = remote_omni_postgresql_password, dbname = 'mvhbdgdk', host = 'manny.db.elephantsql.com')
```
Using this R connection, write and execute a query to return all the wrestlers from the wrestlers table.
```{r}
#Check what tables db contains
dbListTables(conn = wrestling_remote_db_connection)
#check all fields (columns)
dbListFields(conn = wrestling_remote_db_connection, name = "wrestlers")
```
Now return all wrestlers
```{r}
remote_wrestlers <- dbGetQuery(conn = wrestling_remote_db_connection, 
                               statement = 
                                 "SELECT * FROM wrestlers")
remote_wrestlers
```






```{r}
#close remote db once finished working with it.
dbDisconnect(conn = remote_wrestlers)
```




