---
title: "Distributions homework"
output: html_notebook
---

```{r}
library(janitor)
library(tidyverse)
```
```{r}
data_set <- read_csv("data/20190928-items.csv")
#View(data_set)
```
```{r}
clean_data_set <- data_set %>%
  clean_names()
names(clean_data_set)
```
```{r}
most_phones <- clean_data_set %>%
  group_by(brand) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```
```{r}
# plot histogram of ratings for Samsung phones.
clean_data_set %>%
  filter(brand == "Samsung") %>%
  ggplot(aes(x = rating)) + 
  geom_histogram(aes(y = ..density..), col = "white", bins = 30) + 
  #apply normal distribution overlay
  stat_function(
    fun = dnorm,
    args = list(
      mean = mean(clean_data_set$rating),
      sd = sd(clean_data_set$rating)
    ),
    col = "black"
  )
  
```

```{r}
clean_data_set %>%
  filter(brand == "Samsung") %>%
  ggplot(aes(x = rating)) + 
  geom_histogram(aes(y = ..density..), col = "white", bins = 5) + #reducing the number of bins (e.g. to 5) makes this dataset look more like normal distribution. 
  #apply normal distribution overlay
  stat_function(
    fun = dnorm,
    args = list(
      mean = mean(clean_data_set$rating),
      sd = sd(clean_data_set$rating)
    ),
    col = "black"
  )
```
I understood that a normal distribution can be fitted over any dataset. In case of the mobile phone ratings, I think the model does fit reasonably well inside normal distribution, except for outliers. 

If I am only looking at plots, it looks like reducing number of bins (making bins wider) makes the data look more "normalized" and fit better under the bell shaped normal distribution. 

In terms of the next question - calculating propotions of data 1, 2 or 3 SDs away from the mean, I have absolutely no idea what is what. 

However, I can calculate the mean value and sd and I hope I understand the concept of Standard deviation correctly.
```{r}
# Calculate mean and sd of the ratings

stats_of_ratings <- clean_data_set %>%
  filter(brand == "Samsung") %>%
  summarise(total_ratings = n(),
            average_rating = mean(rating),
            sd = sd(rating))
stats_of_ratings
```
```{r}
prop_of_ratings <- clean_data_set %>%
  filter(rating>= stats_of_ratings$average_rating - (stats_of_ratings$sd*2)) %>%
  filter(rating<= stats_of_ratings$average_rating + (stats_of_ratings$sd*2)) %>%
  summarise(within_one_sd_prop = stats_of_ratings$total_ratings / n())

prop_of_ratings
```


