---
title: "Gleb's homework 30/06/2020"
output: html_notebook
---

<h1>Part 1.</h1>

<h2>Q1.</h2>

Create a vector called stock_prices with the following data points: 23, 27, 23, 21, 34, 24, 25, 30, 37, 30.
```{r}
stock_prices <- c(23, 27, 23, 21, 34, 24, 25, 30, 37, 30)
```
Create a vector called day_of_week, which repeats Monday to Friday twice. i.e. ‘Monday’, ‘Tuesday’, ‘Wednesday’, ‘Thursday’, ‘Friday’, ‘Monday’, ‘Tuesday’, ‘Wednesday’, ‘Thursday’, ‘Friday’.
```{r}
day_of_week <- rep(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"),2)
```
<h2>Q2.</h2>

Create a vector called day_of_week_factor, which has the same data as day_of_week, but is of factor type.
```{r}
day_of_week_factor <- as.factor(day_of_week)
```
Create a vector called named_stock_prices, which contains the stock prices, named by days of the week.
```{r}
names(stock_prices) <- day_of_week_factor
named_stock_prices <- stock_prices
named_stock_prices
```
This was difficult for me and my code seems to be super inefficient, but it works :)

<h2>Q3.</h2>

Make a data frame called stock_data containing the stock price and day of the week information, and View() the result.
```{r}
stock_data <- data.frame(day_of_week, stock_prices)
View(stock_data)
```

<h2>Q4.</h2>

Make a list called stock_list with named elements as follows: the vector of stock_prices, the vector day_of_week, and the data frame you made in question 3. Choose sensible names for the list elements.
```{r}
stock_list <- list(
  day = day_of_week_factor,
  price = stock_prices
)
stock_list

```
<h1>Part 2</h1>

<h2>Q1.</h2>

Select the 4th, 5th and 6th stock prices from stock_prices.
```{r}
stock_prices[4:6]
```
Select the stock prices greater than 30 from stock_prices.
```{r}
stock_prices[stock_prices > 30]
```
<h2>Q2.</h2>

Select the day_of_week column from the stock_data data frame.
```{r}
stock_data$day_of_week
```
Select the rows of the stock_data data frame where the stock_prices are less than 25.
```{r}
subset(stock_data, stock_prices < 25)
```
Select the 1st column of stock_data.
```{r}
stock_data[, 1]
```
Select the 3rd row of stock_data.
```{r}
stock_data[3, ]
```
Select the 3rd element in the 1st column of stock_data.
```{r}
stock_data[3, 1]
```

```{r}
stock_data
```

<h2>Q3.</h2>
Select the data frame from within the list of stocks.
```{r}
data.frame(stock_list)
```
<h1>Extension</h1>

Download the tidyquant library.

<code> install.packages("tidyquant")

library(tidyquant)</code>
```{r include=FALSE}
install.packages("tidyquant")
library(tidyquant)
```
Use it to get stock prices from a company of your choice from the current year. You’ll need to look up the help file to do this.
```{r}
help(package = "tidyquant")
```
```{r}
apple_stock <- data.frame(getYahooData("AAPL", 20200101, freq = "monthly", adjust = FALSE))
apple_stock
```
Edit the data frame to keep only the date and close columns.
```{r}
apple_stock$Close
```
But I could not assign a column name to the first column.

Subset to find the rows at which the close price is higher than average.
```{r}
mean_value <- mean(apple_stock$Open, apple_stock$High, apple_stock$Low, trim = 1)
subset(apple_stock, apple_stock$Close > mean_value)
```