---
title: "Tidy day 1 homework"
output: html_notebook
---
load Tidyverse
```{r}
library(tidyverse)
```

Q1. Load in the dataset and have a look at it. What are the dimensions, variable types, variable names, etc

```{r}
Starbucks_calories <- read_csv("homework/data/starbucks_drinkMenu_expanded.csv")
#view(Starbucks_calories)
dim(Starbucks_calories)
names(Starbucks_calories)
```
Q2. Let’s first investigate the calories of different drinks. Select the variables Beverage_category, Beverage, Beverage prep and Calories from your data. Since we are interested in the calorie content, check if there are any NA values in the data, and drop them if there are.
```{r}
drinks_calories <- select(Starbucks_calories, Beverage_category:Calories) %>%
#filter(Calories != "NA")
drop_na(Calories)
drinks_calories
```
Q3. Create a new variable (column) called calorie_diff, which stores the difference between 135 calories (135 calories = 10 cubes of sugar!) and the calories in each drink. (hint: you’ll want to subtract the calories from 135 to see which drink have more or less than 10 cubes of sugar).
```{r}
calorie_diff <- mutate(drinks_calories, 
                     calorie_diff = (Calories - 135) / 10)
view(calorie_diff)
```
Q4. Summarise the mean number of calories in each beverage_category. Which 3 drinks have the most calories? Which 3 drinks have the least? Write a small summary of your findings.
```{r}
# beverage_category_groups <- group_by(calorie_diff, Beverage_category) %>%
# summarise(beverage_category_groups, Beverage_category, mean_calories = 
#             mean(Calories)) %>%
#   select(c("Beverage_category", "mean_calories"))
beverage_category_groups <- group_by(calorie_diff, Beverage_category)
beverage_category_summarised <- summarise(beverage_category_groups, calories_mean = 
                                            round(mean(Calories),digits = 0))
arrange(beverage_category_summarised, calories_mean)
#unique(drinks_calories$Beverage_category)
```
# Brief Summary of findings:
Smoothies, 
Frappuccino® Blended Coffee
and Signature Espresso Drinks
are the three drinks with the highest calorie content. 
--
Without any further analysis I could hypothesise that Smoothies have the highest calorie content of all drinks because they are high in sugar. The other two high calorie content drinks are made with milk (which is high in calories due to fat).
---
Coffee,
Shaken Iced Beverages 
and Classic Espresso Drinks
are lowest in calories. 
--
These are usually made without or only a little milk.

Q5. Let’s look at this a different way. What is the average number of calories in each Beverage_prep type?
```{r}
beverage_prep_groups <- Starbucks_calories %>%
  group_by(Beverage_prep) %>%
  summarise(calories_mean = round(mean(Calories),digits = 0)) %>%           
  arrange(calories_mean)

beverage_prep_groups
#unique(calorie_diff$Beverage_prep)
```

Q6. Which Beverage_prep type contains more than the average calories of all drinks?
Hint: to answer this, you’ll have to first figure out what the average calories across all drinks are, and then use that as a filter for the grouped Beverage_prep data.
```{r}
average_calories <- mean(drinks_calories$Calories)
average_calories

above_average_calories_by_prep <- Starbucks_calories %>%
  group_by(Beverage_prep) %>%
  summarise(calories_mean = round(mean(Calories), digits = 0)) %>%
  mutate(compared_to_average = 
           ifelse(average_calories > calories_mean, "Lower than average", 
                  "Higher than average")) %>%
  arrange(desc(calories_mean))

above_average_calories_by_prep
```

Q7. Which is the best type of coffee drink to get if you’re worried about consuming too many calories?
```{r}
lowest_calorie_drink <- Starbucks_calories %>%
  select(c("Beverage", "Calories")) %>%
  arrange(Calories) %>%
  head(1)

lowest_calorie_drink
```












