---
title: "Gleb V homework 01/07/2020"
output: html_notebook
---
#beer data
```{r}
#get beer data
beer_data <- CodeClanData::beer
head(beer_data, 2)
```
```{r}
beer_data[order(beer_data$percent, decreasing = TRUE), ]
mean(beer_data$percent)
median(beer_data$percent)
```
#Facts about beer_data

1. The highest alcohol content beer is "Flying Dog Double Dog xca, with 11.5 %abv.

2. The average alcohol content is around 5.2%, and median is 4.9%. This tells me that people prefer beers with higher alcohol content. (Using demand/supply logic)


#temp data
```{r}
#get temp data
temp_data <- CodeClanData::temp
years <- (1910:2015)
rownames(temp_data) <- years
annual_temp <- t(temp_data)
annual_temp
```
Average monthly temperatures.
```{r}
mean_monthly <- colMeans(temp_data)
mean_monthly
```
Average, avg coldest, avg, warmest annual temperatures.
```{r}
mean_annual <- rowMeans(temp_data)
mean_annual
coldest_temp_year <- list("The lowest average temperature of ", min(mean_annual), "degrees C was recorded in", years[min(mean_annual)])
paste(coldest_temp_year, collapse = " ")
warmest_temp_year <- list("The warmest average temperature of ", max(mean_annual), "degrees C was recorded in", years[max(mean_annual)])
paste(warmest_temp_year, collapse = " ")
```

(cheating) The summary of the temp_data matrix by month for all sorts of interesting insights arranged by month.
```{r}
summary(temp_data)
```
```{r}
plot(years, mean_annual, 
     main = "Mean temperature",
     ylab = "Mean temp in degrees C")
```

#Facts about temp_data:

1. From the above chart it is clearly visible that in the given period the mean annual temerature is rising.

2. In May the the temperature seems to be the most predictable with mean and median averages lieng within 0.01 degrees, which indicates that May is least likely to record extreme temperatures.


#GoT data
```{r}
#get game_of_thrones data
got_data <- CodeClanData::game_of_thrones
got_data$characters[4]
```
#GoT facts

1. There are 434 charachters in the book.

2. name: Margaery Tyrell, gender: Female











