---
title: "Gleb V homework 01/07/2020"
output: html_notebook
---
#beer data
```{r}
#get beer data
beer_data <- CodeClanData::beer
head(beer_data, 2)
```
```{r}
beer_data[order(beer_data$percent, decreasing = TRUE), ]
mean(beer_data$percent)
median(beer_data$percent)
```
#Facts about beer_data
1. The highest alcohol content beer is "Flying Dog Double Dog\xca", with 11.5 %abv.
2. The average alcohol content is around 5.2%, and median is 4.9%. This tells me that people prefer beers with higher alcohol content. (Using demand/supply logic)


#temp data
```{r}
#get temp data
temp_data <- CodeClanData::temp
years <- (1910:2015)
rownames(temp_data) <- years
```
Arrange years by average temperature from warmest to coldest.
```{r}
mean_temp <- rowMeans(temp_data)
coldest_to_warmest <- order(mean_temp, decreasing = TRUE) #wrong vector name
years[coldest_to_warmest]
```
(cheating) The summary of the temp_data matrix by month for all sorts of interesting insights arranged by month.
```{r}
summary(temp_data)
```
```{r}
plot(years, mean_temp, main = "Mean temperature",
     ylab = "Mean temp in degrees C")
```

#Facts about temp_data:
1. In the given period I the mean temerature is rising, but the rise is not linear
2. In May the the temperature seems to be the most predictable with mean and median averages lieng within 0.01 degrees, which indicates that May is least likely to record extreme temperatures.



#GoT data
```{r}
#get game_of_thrones data
got_data <- CodeClanData::game_of_thrones
got_data$characters[4]
```
#GoT facts
1. There are 434 charachters in the book.
2. name: Margaery Tyrell, gender: Female











