---
title: "Gleb V homework 2020-07-06"
output: html_notebook
---

Read in the state_income_data.csv file using the appropriate function.
```{r}
#import library "readr"
library(readr)
library(dplyr)
#load JSON library too
library(jsonlite)
#load library to deal with excel
library(readxl)
```

```{r}
head(read_csv("data/state_income_data.csv")) #read file
```
How do you specify your own column names when using read_csv()
```{r}
#skip one (first row of the raw dataset, specify custom variable names (column names),  making sure that total number of variables(columns) matches the raw dataset
state_income_data <- read_csv("data/state_income_data.csv", skip = 1, 
                              col_names = c("first_letter", "state", "2002", "2003",
                                            "2004", "2005", "2006",
                                            "2007", "2008", "2009", "2010", "2011",
                                            "2012", "2013", "2014", "2015"))
state_income_data
```
Read in the cars.csv file and use the col_types() function to ensure you load in:
X1 as character
mpg, cyl, disp, hp as double
vs as logical
```{r}
#load raw file
cars_raw <- read_csv("data/cars.csv")
#check variable types first
str(cars_raw)
```
```{r}
#variable types are alreay specified correctly, except for variable "vs", change it to logical type
#read in cars dataset and change variable vs type to logical
cars_raw <- read_csv("data/cars.csv", col_types = cols(vs = col_logical()))
hcars_raw
str(cars_raw)
```
Read in the scotland.txt file using the appropriate function.
```{r}
#read file and assign it to object "scotland"
scotland <- read_tsv("data/scotland.txt")
scotland
```
```{r}
#this file seems to be delimited by tab and ";" and it has "Edinburgh" in the first row. I can convert it to list, without losing "Edinburgh"
scotland_list <- lapply(scotland, strsplit, split = ";")
scotland_list
```
```{r}
#alternatively I can skip the first row and do away with "Edinburgh"
scotland_df <- read_delim("data/scotland.txt", skip = 1, delim = ";")
scotland_df
```

How do you read text into a one element character vector? - Using read_file()
```{r}
s_v <- read_file("data/scotland.txt")
s_v
```
Read in the steam-200k-sample.csv file. Fix any problems you may encounter.
```{r}
#open file in excel, first 4 rows have unneccessary data, variable "bought online" should be logical.

#read in file skipping first 4 rows and changing variable type.
steam_raw <- read_csv("", skip = 4, col_types = cols("bought online" = col_logical()))
#rename variables (columns) for easier processing in the future.
data.table::setnames(steam_raw, old = c("customer id", "game name", "bought online"), 
                     new = c("customer_id", "game_name", "bought_online"))
steam_raw
```
Read in the historic_eu_payments.tsv file.
```{r}
eu_payments <- read_tsv("data/historic_eu_payments.tsv")
eu_payments
```
How do you read lines of text into a multi-element text vector? - read_lines()

Read in the JSON file from the following url: http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt
```{r}
jsread <- read_file("http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt")
jsread_pretty <- prettify(jsread) 
jsread_parse <- parse_json(jsread)
jsread_df <- fromJSON(jsread)
jsread_df1 <- lapply(jsread_parse, as.data.frame)
jsread_df

```

A lot of Excel sheets you will encounter will contain more than one sheet. Try to write some code that reads in all the different sheets in the file green_bindle_consulting.xlsx.

```{r}
#this is code I found on StackOverflow
#these functions use the library(readxl)
read_excel_allsheets <- function(filename, tibble = FALSE) {
#Tidyverse tibble can be used (the default with read_excel), then should be tibble = TRUE
  sheets <- excel_sheets(filename)
  x <- lapply(sheets, function(X) read_excel(filename, sheet = X))
  if(!tibble) x <- lapply(x,  as.data.frame) #can be output as list: lapply(x,  as.list)
  names(x) <- sheets
  return(x)
}
read_excel_allsheets("data/green_bindle_consulting.xlsx")
```

```{r}
#this is my own attempted solution
gbc <- read_xlsx("data/green_bindle_consulting.xlsx", sheet = sheet)
num_steets <- length(excel_sheets("data/green_bindle_consulting.xlsx"))
sheet_num <- 1
all_sheets <- c()
while(sheet_num <= num_steets){
  read_xlsx("data/green_bindle_consulting.xlsx", sheet = sheet_num)
     all_sheets <- c(all_sheets, sheet)
     sheet_num + 1
}
```


