---
title: "SQL Lab 2020-07-08"
output: html_notebook
---
Import SQL library
```{r}
library(RPostgreSQL)
```
Create root path and connect to credentials
```{r}
credentials_location <- paste0(Sys.getenv("HOME"),"/credentials.R")
source(credentials_location)
```
Create DB connection
```{r}
db_conect <- dbConnect(drv = PostgreSQL(), user = postgresql_username, password = postgresql_password, dbname = "omni_employees", host = "localhost")
rm(postgresql_username, postgresql_password, remote_omni_postgresql_password, remote_omni_postgresql_username)
```
Check if connetion was successful and list all tables
```{r}
dbListTables(conn = db_conect)
```
```{r}
dbListFields(conn = db_conect, name = "employees")
```

# Lab

Find all employees working in the HR.
```{sql connection=db_conect}
SELECT *
FROM employees
WHERE department = 'Human Resources';
```
Get names (f & l) and country of the Legal dept employees
```{sql connection=db_conect}
SELECT 
  first_name,
  last_name,
  country
FROM employees
WHERE department = 'Legal';
```

how many employees are based in Portugal.
```{sql connection=db_conect}
SELECT
 COUNT(id) AS num_employees_in_portugal
FROM employees
WHERE country = 'Portugal';
```

how many employees are based in Portugal or Spain
```{sql connection=db_conect}
SELECT 
  COUNT(id) AS total_employees_in_portugal_or_spain
FROM employees
WHERE country IN ('Portugal', 'Spain');
```

count records in pay_details where local_account_no is NULL
```{sql connection=db_conect}
SELECT 
  COUNT(id) count_of_missing_local_account_details
FROM pay_details
WHERE local_account_no IS NULL;
```
check if there are any records without local_account_no and iban
```{sql connection=db_conect}
SELECT 
  id, 
  local_account_no,
  iban
FROM pay_details
WHERE local_account_no IS NULL AND iban IS NULL;
```
list all employees (f & l names) by l name aplhabetically, dont show null vaslues.
```{sql connection=db_conect}
SELECT
  first_name,
  last_Name
FROM employees
ORDER BY LOWER(last_name) ASC NULLS LAST;
```
list of employees first names, last names and countries, ordered alphabetically first by their country and second by their last name (put any nulls last).
```{sql connection=db_conect}
SELECT 
  first_name,
  last_name,
  country
FROM employees
ORDER BY country ASC, UPPER(last_name) ASC NULLS LAST;
  
```


find top 10 highest paid employees
```{sql connection=db_conect}
SELECT *
FROM employees
ORDER BY salary DESC NULLS LAST
LIMIT 10;
```

find fname lname and salary of the lowest paid employees in Hungary
```{sql connection=db_conect}
SELECT
  first_name,
  last_name,
  salary
FROM employees
WHERE country = 'Hungary'
ORDER BY salary ASC NULLS LAST
LIMIT 1;
```


```{sql connection=db_conect}
SELECT * 
FROM employees
WHERE country = 'Hungary';
```

count employees whos fname starts with "F"
```{sql connection=db_conect}
SELECT 
  COUNT(id) AS number_of_F_employees 
FROM employees
WHERE UPPER(first_name) LIKE 'F%';
```
get all details of all employees with "yahoo" email.
```{sql connection=db_conect}
SELECT *
FROM employees
WHERE LOWER(email) LIKE '%yahoo%';
```

how many employees not in France or Germany are enrolled in pension
```{sql connection=db_conect}
SELECT 
  COUNT(id) AS number_of_employees_enrolled_in_pension
FROM employees
WHERE country NOT IN ('France', 'Germany') AND pension_enrol = TRUE;
```

get a breakdown of numbers of employees enrolled/not enrolled/unknown in the pension plan.

```{sql connection=db_conect}
SELECT
  pension_enrol,
  COUNT(id) AS pension_enrol_count
FROM employees
GROUP BY pension_enrol;
```
find max engineering dept salary who work 1.0 fte
```{sql connection=db_conect}
SELECT 
  MAX(salary) 
FROM employees
WHERE department = 'Engineering' AND fte_hours = '1.0';
```
how many employees who started in 2003 are working in each dept
```{sql connection=db_conect}
SELECT 
  department,
  COUNT(id) AS number_of_employees
FROM employees
WHERE EXTRACT(YEAR FROM start_date) = 2003
GROUP BY department
ORDER BY number_of_employees DESC;
```


disconnect from db before finishing the project.
```{r}
dbDisconnect(db_conect)
```



