---
title: "Model building homework"
output: html_notebook
---
```{r}
library(tidyverse)
```


```{r}
house_data <- read_csv("data/kc_house_data.csv")
glimpse(house_data)
summary(house_data)
```

You might like to think about removing some or all of date, id, sqft_living15, sqft_lot15 and zipcode (lat and long provide a better measure of location in any event).

```{r}
house_data_tidy <- house_data %>%
  mutate(waterfront = ifelse(waterfront == 1, TRUE, FALSE),
         renovated = ifelse(yr_renovated == 0, FALSE, TRUE)) %>%
  select(-c(id, date, sqft_living15, sqft_lot15, yr_renovated))
glimpse(house_data_tidy)
```

* I kept zipcode, because it is likely to provide easier overview of how the price varies based on location in the city. I changed waterfront to logical and yr_renovated to logical renovated. 

condition is a categorical variable on a scale 1 - 5. 
```{r}
sort(unique(house_data$condition))
```
grade is also categorical on a scale 1 - 13, however grade 2 is not present.
```{r}
sort(unique(house_data$grade))
```

Check for aliased variables

```{r}
alias(lm(price ~ ., data = house_data_tidy))
```

It looks like variables sqft_living and sqft_above are aliased, so I will remove sqft_above from the model.

```{r}
house_data_tidy <- house_data_tidy %>%
  dplyr::select(-c(sqft_above))
alias(lm(price ~ ., data = house_data_tidy))
glimpse(house_data_tidy)
```

Systematically build a regression model containing up to four main effects (remember, a main effect is just a single predictor with coefficient), testing the regression diagnostics as you go.

```{r}
library(GGally)
```
```{r}
ggpairs(house_data_tidy)
```

ggpairs plot is not at all helpful :(

```{r}
summary(lm(price ~ ., data = house_data_tidy))
```

I will attempt to build a model with following features: sqft_living, lat, grade, waterfront, view.  

```{r}
model1a <- lm(price ~ sqft_living, data = house_data_tidy)
summary(model1a)
```
```{r}
library(ggfortify)
autoplot(model1a)
```
```{r}
par(mfrow = c(2,2))
plot(model1a)
```
```{r}
model1b <- lm(price ~ lat, data = house_data_tidy)
summary(model1b)
```
```{r}
par(mfrow = c(2,2))
plot(model1b)
```
```{r}
model2a <- lm(price ~ sqft_living + waterfront, data = house_data_tidy)
summary(model2a)
```
```{r}
par(mfrow = c(2,2))
plot(model2a)
```

```{r}
model2b <- lm(price ~ sqft_living + view, data = house_data_tidy)
summary(model2b)
```

```{r}
par(mfrow = c(2,2))
plot(model2b)
```


```{r}
model2c <- lm(price ~ sqft_living + renovated, data = house_data_tidy)
summary(model2c)
```

```{r}
par(mfrow = c(2,2))
plot(model2c)
```


```{r}
anova(model1a, model2b)
```

```{r}
model3a <- lm(price ~ sqft_living + view + waterfront, data = house_data_tidy)
summary(model3a)
```

```{r}
par(mfrow = c(2,2))
plot(model3a)
```

```{r}
model3b <- lm(price ~ sqft_living + view + renovated, data = house_data_tidy)
summary(model3b)
```

```{r}
par(mfrow = c(2,2))
plot(model3b)
```


```{r}
model3c <- lm(price ~ sqft_living + view + grade, data = house_data_tidy)
summary(model3c)
```
```{r}
par(mfrow = c(2,2))
plot(model3c)
```
```{r}
anova(model2b, model3c)
```

```{r}
model4a <- lm(price ~ sqft_living + view + grade + lat , data = house_data_tidy)
summary(model4a)
```

```{r}
par(mfrow = c(2,2))
plot(model4a)
```

```{r}
model4b <- lm(price ~ sqft_living + view + grade + yr_built, data = house_data_tidy)
summary(model4b)
```

```{r}
par(mfrow = c(2,2))
plot(model4b)
```



* model1a: price ~ sqft_living RSE: 261500, r-squared: 0.4929, not too satisfied with Residuals vs Fitted plot (top heavy), scale location is skewed, Residuals vs Leverage are over Cook's distance. 
* model1b: price ~ waterfront RSE: 349400, r-squared: 0.09425, looks better on diagnostic chart.

***model1a seems overall better based on r-sqared value***
 
* model2a: price ~ sqft_living + waterfront RSE: 251500, r-sq: 0.5307
* model2b: price ~ sqft_living + view       RSE: 250300, r-sq: 0.5353
* model2c: price ~ sqft_living + renovated  RSE: 259500, r-sq: 0.5005

***model2b seems overal better due to r-sq***

* model3a: price ~ sqft_living + view + waterfront RSE: 246100, r-sq: 0.5507
* model3b: price ~ sqft_living + view + renovated RSE: 249000, r-sq: 0.54
* model3c: price ~ sqft_living + view + grade     RSE: 240000, r-sq: 0.5725

***model3c seems better based on overall r-sq*** 

* model4a: price ~ sqft_living + view + grade + lat      RSE: 221500, r-sq: 0.636
* model4b: price ~ sqft_living + view + grade + yr_built RSE: 224800, r-sq: 0.625

***model4a is better due to r-sq and diagnostic chart***


Consider possible interactions between your four main effect predictors and test their effect upon r2. Choose your best candidate interaction and visualise its effect.


```{r}
interact_model <- lm(price ~ sqft_living : grade + view + lat, data = house_data_tidy)
summary(interact_model)
```

price ~ sqft_living : grade + view + lat : r-sq: 0.6701 is the best candidate for interacting features

```{r}
price_resid<- house_data_tidy %>%
  add_residuals(model4a)%>%
  dplyr::select(-price)

coplot(resid ~ sqft_living | grade + view + lat, data = price_resid, columns = 3)
```
not sure about the above chart


Calculate the relative importance of predictors from your best 4-predictor model (i.e. the model without an interaction). Which predictor affects price most strongly?

```{r}
library(relaimpo)
```
```{r}
calc.relimp(model4a, type = "lmg", rela = TRUE)
```





















