---
title: "Gleb V weekend homework 04/07/2020"
output: html_notebook
---

#Control flow

##if statements and functions.

Write a function which multiples all numbers by 15 and adds 4.

```{r}
mult_by_15_add_4 <- function(x = NULL){
  if(is.null(x)|!is.numeric(x)){
    return("Please enter numeric value")
  } else {
    by_15 <- x * 15
    add_4 <- by_15 + 4
  }
  return(add_4)
}
mult_by_15_add_4(1)
mult_by_15_add_4(2)
mult_by_15_add_4(3)
mult_by_15_add_4()
mult_by_15_add_4("two")
```

Write a function that returns “bird”, if the input is “goose”, “duck” or “pigeon”, and returns “not bird” for all other input.
```{r}
#correct basic version
is_bird <- function(x = "no_value"){
  if(x == "no_value"){
    return("Plese enter some text")
  } else {
    dplyr::case_when(
    x == "goose" ~ paste("bird"),
    x == "duck" ~ paste("bird"),
    x == "pigeon" ~ paste("bird"),
    TRUE ~ paste("not bird")
    )
  }
}

is_bird()
is_bird("Pterodactyl")
is_bird("Sparrow, surely it's a bird, lets see...")
is_bird("goose")
is_bird("duck")
is_bird("pigeon")
```

```{r}
#having an explicit return statement after case_when produces erroneous output.
is_bird <- function(x = "no_value"){
  input <- c(x)
  if(input == "no_value"){
    return("Plese enter some text")
  } else {
    #needs an object assignment to case when, then return object:
    # output <- 
    dplyr::case_when( 
    input == "goose" ~ paste("bird"),
    input == "duck" ~ paste("bird"),
    input == "pigeon" ~ paste("bird"),
    TRUE ~ paste("not bird")
    )
  }
  return(input) # change return argument to output
}

is_bird()
is_bird("Pterodactyl")
is_bird("Sparrow, surely it's a bird, lets see...")
is_bird("goose")
is_bird("duck")
is_bird("pigeon")
```
Write a function which multiplies all numbers by 10. If the input isn’t a number, the function should return “Invalid input”.
```{r}
by_ten <- function(x){
  if(is.null(x) | !is.numeric(x)){
    error_msg <- c("Invalid input")
    return(error_msg)
  } else { 
    result <- x * 10
    return(result)
    }
}
by_ten(2)
by_ten(5.3)
by_ten("x")
by_ten(7)
```
For the vector below, make a new vector which is equal to “Big” every time the element of sizes is greater than 10, and equal to “Small” every time the element of sizes is less than or equal to 10.
```{r}
sizes <- c(13, 15, 10, 8, 22)
new_vector <- ifelse(sizes > 10, "Big", sizes)
new_vector
```
For the vector below convert:
apple → alpaca, banana → bonobo, cherry → chipmunk
```{r}
fruit <- c("apple", "apple", "banana", "cherry", "cherry")
not_fruit <- dplyr::recode(fruit, "apple" = "alpaca", 
                           "banana" = "bonobo", 
                           "cherry" = "chipmunk")
not_fruit

```
Create a new vector which is equal to:
“Wife older” whenever the wife’s age is highest “Husband older” when the husband’s age is highest “Same age” when they are the same age.
```{r}
wife_age <- c(29L, 30L, 36L, 31L, 22L)
husband_age <- c(28L, 35L, 32L, 31L, 29L)

comparison <- dplyr::case_when(
  wife_age > husband_age ~ paste("Wife older"),
  wife_age < husband_age ~ paste("Husband older"),
  wife_age == husband_age ~ paste("Same age")
)
data.frame(wife_age, comparison, husband_age)
```
# Loops
```{r}
my_list <- list(
  4,
  "apple",
  10.5,
  c("is", "an", "apple"),
  "apple",
  c("i", "like", "apples"),
  8
)
class(my_list[[2]][1])
my_list
```
Use a loop to print out every element of my_list which is of type character. Decide if you need a for loop or a while loop.
```{r}
for(char in my_list){
  if (class(char) == "character") {
    print(char)
  }
}
```
Once again write a loop that prints out character elements. This time if the element has a length() greater than one, paste() all the elements in that vector together into one big character vector.
```{r}
to_fill <- c()
for (item in my_list) {
  if(length(item) > 2){
    to_fill <- c(to_fill, item)
  }
}
print(to_fill)
class(to_fill)
```


# Extension

Write code that prints a multiplication table for numbers up to 12. i.e. there will be 12 rows and 12 columns, and each element should be the row number multiplied by the column number.
```{r}
iter_val<- 1 #sequence start 
stop_val <- 144 #sequence stop
matrix_vec <- c() #each iteration  of the loop adds one number to the vector

while(iter_val <= stop_val) { #sequence stops after 144 iterations
  #each number is multiplied by 12 as it is appended to the vector
  matrix_vec <- c(matrix_vec, iter_val * 12) 
  #increases iterable value by one
  iter_val <- iter_val + 1 
}
#convert vector to matrix of 12rows and 12 columns
matrix_final <- matrix(matrix_vec, nrow = 12, ncol = 12, byrow = FALSE) 
#display matrix
matrix_final 
```
Not Completed --
Write a function that takes a vector, and creates a text art histogram.
You may want to use the function cat(). This is similar to print(), but prints directly, without vector markers. You can also include newlines "\n" when using cat().--
-----
By considering the terms in the Fibonacci sequence whose values do not exceed four million, find the sum of the even-valued terms.




