---
title: "Logistic Regression hw"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
```

```{r}
juice <- read_csv("data/orange_juice.csv") %>%
  clean_names() %>%
  mutate(
    special_ch = ifelse(special_ch == 1, TRUE, FALSE),
    special_mm = ifelse(special_mm == 1, TRUE, FALSE),
    store7 = as.factor(store7),
    weekof_purchase = as.factor(weekof_purchase), 
    store_id = as.factor(store_id),
    purchase_mm = ifelse(purchase == "MM", TRUE, FALSE),
    ) %>%
  select(-c(purchase, store, store7)) # I chose to remove these variable right away as they are already represented in the dataset in other columns.

juice
summary(juice)
unique(juice$store)
```

```{r}
library(GGally)
```
```{r}
pairs1 <- c("purchase_mm", "weekof_purchase", "store_id", "price_ch")
pairs2 <- c("purchase_mm", "price_mm", "disc_ch", "disc_mm")
pairs3 <- c("purchase_mm", "special_ch", "special_mm", "loyal_ch")
pairs4 <- c("purchase_mm", "sale_price_mm", "sale_price_ch", "price_diff")
pairs5 <- c("purchase_mm", "pct_disc_mm", "pct_disc_ch", "list_price_diff")
```

```{r}
juice %>%
  select(purchase_mm, weekof_purchase) %>%
  ggpairs(cardinality_threshold = 52, report = FALSE)

juice %>%
ggplot(aes(x = weekof_purchase, y = purchase_mm)) +
  geom_col()
#there seems to be quite a lot of variability in purchase_mm depending on weekof_purchase, therefore I will keep weekof_purchase variable.

juice %>%
  select(pairs1) %>%
  ggpairs(cardinality_threshold = 52, report = FALSE)
#weekof_purchase, store_id

juice %>%
  select(pairs2) %>%
  ggpairs(report = FALSE)
#price_mm, disc_mm

juice %>%
  select(pairs3)%>%
  ggpairs(report = FALSE)
#special_ch, special_mm, ?loyal_ch

juice %>%
  select(pairs4) %>%
  ggpairs(report = FALSE)
#sale_price_ch, store7

juice %>%
  select(pairs5) %>%
  ggpairs(report = FALSE)
#pct_disc_mm
```
I think, if I was building a model manually, I would use the following variables: weekof_purchase, store_id, price_mm, disc_mm, special_ch, special_mm, sale_price_ch, pct_disc_mm, loyal_ch.

But I am finding it hard to understand, so I will make an automated feature selection.

```{r}
#create training & testing datasets
n_data <- nrow(juice)
test_index <- sample(1:n_data, size = n_data*0.1)

test_juice <- slice(juice, test_index)
train_juice <- slice(juice, -test_index)
```

```{r}
library(modelr)
library(pROC)
```


```{r}
#as baseline I will build a model that includes all features
all_feature_model <- glm(purchase_mm~., data = train_juice, 
                         family = binomial(link = "logit"))

all_feature_pred <- train_juice %>%
  add_predictions(all_feature_model, type = "response")


roc_all_feature_model <- all_feature_pred %>%
  roc(response = purchase_mm, predictor = pred)

roc_curve_all_feature <- ggroc(data = roc_all_feature_model, legacy.axes = TRUE)
coord_fixed()

alias(all_feature_model)

roc_curve_all_feature

```


```{r}
#secondly I will attempt to plot my selected features
manual_feature_check <- glm(purchase_mm ~ weekof_purchase + store_id + price_mm + disc_mm + special_ch + special_mm + sale_price_ch + pct_disc_mm + loyal_ch, data = train_juice, family = binomial(link = "logit"))

manual_feature_pred <- train_juice %>%
  add_predictions(all_feature_model, type = "response")

roc_manual_feature_model <- manual_feature_pred %>%
  roc(response = purchase_mm, predictor = pred)

roc_curve_manual_feature <- ggroc(data = roc_manual_feature_model, legacy.axes = TRUE)
coord_fixed()

alias(manual_feature_check)

auc_manual_feature <- auc(roc_manual_feature_model, )

roc_curve_all_feature
auc_manual_feature
```

Curves of both models look almost identical :)

Automated model no interactions

```{r}
library(glmulti)
```

```{r}
auto_all_feature_model <- glmulti(purchase_mm ~ . , #testing effects of all features
                                  data = train_juice, #using training dataset
                                  level = 1, # main effects only, no interactions
                                  method = "h", #exhaustive search
                                  crit = "bic", 
                                  confsetsize = 10, #keeping only best 10 models
                                  plotty = FALSE, #no plotting during iteration
                                  report = TRUE, #report progress during iteration
                                  fitfunction = "glm",
                                  family = binomial(link = "logit")
                                  )

summary(auto_all_feature_model)
```
Best model has been identified as: purchase_mm ~ loyal_ch + price_diff

```{r}
auto_all_feature_model_w_int <- glmulti(purchase_mm ~ . , #testing effects of all features
                                  data = train_juice, #using training dataset
                                  level = 2, # include interactions
                                  marginality = TRUE, #consider pairs only if features are in the model
                                  method = "h", #exhaustive search
                                  crit = "bic", 
                                  confsetsize = 10, #keeping only best 10 models
                                  plotty = FALSE, #no plotting during iteration
                                  report = TRUE, #report progress during iteration
                                  fitfunction = "glm",
                                  family = binomial(link = "logit")
                                  )
#tried exhaustive search of all features with interactions, but it was taking too long. 

#Trying genetic search with interactions
auto_all_feature_model_w_int_gen <- glmulti(
  purchase_mm ~ .,
  data = train_juice,
  level = 2,               # Interactions considered
  method = "g",            # Genetic algorithm approach
  crit = "aic",            # AIC as criteria
  confsetsize = 10,        # Keep 10 best models
  marginality = TRUE,      # consider pairs only if both main effects in model
  plotty = F, 
  report = T,              # No plots, but provide interim reports
  fitfunction = "glm",     # glm function
  family = binomial(link = "logit")) # binomial family for logistic regression

summary(auto_all_feature_model_w_int)
```



I was only able to run g multi once and it identified the following model: purchase_mm ~ loyal_ch + price_diff. I will stick with it and compare performance to purchase_mm ~ . 


```{r}
auto_model <- glm(purchase_mm ~ loyal_ch + price_diff,
                  data = train_juice, 
                  family = binomial(link = "logit"))

auto_feature_pred <- train_juice %>%
  add_predictions(auto_model, type = "response")

roc_auto_model <- auto_feature_pred %>%
  roc(response = purchase_mm, predictor = pred)

roc_curve_auto_feature <- ggroc(data = roc_auto_model, legacy.axes = TRUE) 
coord_fixed()

alias(auto_model)

auc_manual_feature <- auc(roc_auto_model, )

roc_curve_all_feature
auc_manual_feature
```

Using training dataset, the model "purchase_mm ~ weekof_purchase + store_id + price_mm + disc_mm + special_ch + special_mm + sale_price_ch + pct_disc_mm + loyal_ch" had AUC of 0.9221.

The model "purchase_mm ~ loyal_ch + price_diff" has AUS of 0.9014. 


```{r}
manual_feature_pred_test <- test_juice %>%
  add_predictions(manual_feature_check, type = "response")

roc_manual_feature_model <- manual_feature_pred_test %>%
  roc(response = purchase_mm, predictor = pred)

roc_curve_manual_feature_test <- ggroc(data = roc_manual_feature_model, legacy.axes = TRUE)
coord_fixed()

alias(manual_feature_check)

auc_manual_feature <- auc(roc_manual_feature_model, )

roc_curve_all_feature
auc_manual_feature
```

```{r}
auto_model_test <- glm(purchase_mm ~ loyal_ch + price_diff, 
                       data = test_juice,
                       family = binomial(link = "logit")
                       )

auto_model_test_pred <- test_juice %>%
  add_predictions(auto_model_test, type = "response")

roc_auto_model_test <- auto_model_test_pred %>%
  roc(response = purchase_mm, predictor = pred)

roc_curve_auto_model_test <- ggroc(data = roc_auto_model_test, legacy.axes = TRUE)
coord_fixed()

alias(auto_model_test)

auc_auto_model <- auc(roc_auto_model_test, )

roc_curve_all_feature
auc_manual_feature
```

Manual model AUC using test data was: 0.8666

***I have no idea :(***




