---
title: "Probabilities_homework"
author: "Gleb V"
date: "03/08/2020"
output: html_notebook
---

```{r echo=FALSE}
library(prob)
library(gtools)
library(tidyverse)
options(scipen = 999)
```

# 1. If I roll a six-sided dice once, what is the probability of getting a number less than 5?

I have a total of 6 outcomes. Therefore a chance or rolling anything less (but not equals) than 5 is 6 - 2 = 4. I can roll 1 or 2 or 3 or 4, all of which are less than 5. 

# 2. How many outcomes are there in the sample space of an experiment in which we toss three dice?

Sample space contains all possible outcomes of the experiment, therefore tossing three dice would produce a sample space of 6 x 6 x 6 = 36
```{r}
roll_three_dice <- rolldie(3)
roll_three_dice
```

# In an experiment where we roll four dice:

4 dice produces a sample space of 6 x 6 x 6 x 6 = 1296
```{r}
roll_four_dice <- rolldie(4)
roll_four_dice
```

* how many outcomes are in the event total_equals_5_6_7 (i.e. the total of the four dice equals 5, 6 or 7)? 

There are 4 possible outcomes that result in 5, 10 possible outcomes that result in 6 and 20 outcomes that result in 7, therefore there are 34 possible outcomes. 
```{r}
total_equals_5_6_7 <- roll_four_dice %>%
  mutate(sum_of_rolls = X1 + X2 + X3 + X4) %>%
  filter(sum_of_rolls == 5 | 
           sum_of_rolls == 6 | 
           sum_of_rolls == 7) %>%
  arrange(sum_of_rolls)
total_equals_5_6_7

total_equals_5_6_7_summary <- total_equals_5_6_7 %>%
  group_by(sum_of_rolls) %>%
  summarise(roll_combinations = n())
total_equals_5_6_7_summary
```

* what is the probability of this event?

Probability of the first event `r 4/nrow(roll_four_dice)` + Probability of the second event `r 10/nrow(roll_four_dice)` + Probability of the sum of the third event `r 20/nrow(roll_four_dice)` = `r (4/nrow(roll_four_dice)) + (10/nrow(roll_four_dice)) + (20/nrow(roll_four_dice))`

* what assumptions do we apply in answering part ii? 

Outcomes may not happen in all three events, therefore there is no union of events A & B & C. 


# 4. Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

I'll work out all possible combinations first and count them.

```{r}
people <- 5
chairs <- c("A","B", "C", "D", "E")

people_on_chairs <- permutations(n = 5, r = 5, v = chairs, repeats.allowed = FALSE)
people_on_chairs <- as_tibble(people_on_chairs)
people_on_chairs

nrow(people_on_chairs)

```

There are a 120 possible combinations. There are two possible outcomes where they will sit in order of height: either A, B, C, D, E or E, D, C, B, A. So the probability of them sitting in order is 2/120 (1/60 = 0.01666667) . These outcomes are either left to right or right to left or right to left, which means that there is only one possible combination 1/120, that satisfies our condition. 

The probability of 5 people sitting on 5 chairs in order by hight left to right is 1/120 = 0.008333333

# 5. I roll six dice:

```{r}
roll_six_dice <- rolldie(6)
nrow(roll_six_dice)
```
Rolling 6 dice has a sample space of 46656 possible combinations. 

* what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?

There is only one otcome that satisfies our conditions, which means the probability is 1/46656 = 0.00002143347 (extremely low)

what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?
```{r}
outcome <- c(6,5,4,3,2,1)
roll_six_dice_outcome  <- roll_six_dice %>% 
  filter(isin(., outcome, ordered = FALSE))
roll_six_dice_outcome  
```
There are 720 posssible outcomes where we roll numbers from 1 to 6 regardless of order. Therefore the probability or this happening is 720/46656 = 0.0154321

# 6. If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?

52 cards, 2 colours, 4 suites, therefore I have 52/6.5 = 8 chances of drawing a spade.



